The Ky Fan Norms and Beyond: Dual Norms and Combinations for Matrix Optimization

### 2025-08-24 conf_article/neon.tex
Added logs from NanoGPT speedrun

    Then, we tune F-Muon with $\alpha = 0.5$. Tuned parameters are {\tt lr=0.4(1 - step/total\_steps), momentum=0.65 - 0.1(1 - step/total\_steps), nesterov = True}. While Muon reaches $94.00 \pm 0.13$\% accuracy after 8 epochs, tuned F-Muon reaches $93.97 \pm 0.14\%$ after 8 epochs.

@@

    \subsection{Modded NanoGPT speedrun}
    We test F-Muon on NanoGPT speedrun \citep{modded_nanogpt_2024}.

>>>>

    Then, we tune F-Muon with $\alpha = 0.5$. Tuned parameters are {\tt lr=0.4(1 - step/total\_steps), momentum=0.65, nesterov = True}. While Muon reaches $94.00 \pm 0.13$\% accuracy after 8 epochs, tuned F-Muon reaches $94.01 \pm 0.14\%$ after 8 epochs.

@@

    \subsection{Modded NanoGPT speedrun}
    We test F-Muon on NanoGPT speedrun \citep{modded_nanogpt_2024}. For $\alpha = 0.5$, the optimal parameters are {\tt lr=0.07, momentum=0.95}, while for Muon they were  {\tt lr=0.05, momentum=0.95}. After testing for 1750 steps, as has been done on the speedruns, we get 3.281 cross-entropy loss, while on Muon, it falls below the target threshold 3.28 reaching 3.279.

    TO-DO: more discussions of experiments.
